Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-02-19 ms_pre_post.Rmd
Revise second paragraph

@@

Despite a paucity of theory and resulting predictions, numerous empirical studies on diverse species have found evidence for female inbreeding avoidance. However, only a few such studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms. Among these few studies, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in birds and crickets [e.g., @Pizzari2004; @Simmons2006; @Bretman2009]. An even smaller number of studies comprise sufficient evidence for mechanisms of both pre-copulatory and post-copulatory inbreeding avoidance in two well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015]. A lack of both pre-copulatory and post-copulatory inbreeding has been found in fruit flies [e.g., @Ala-Honkola2011; @Tan2012], and might be reasonably inferred where no evidence of inbreeding avoidance exists [e.g., @Reid2014; @Reid2015]. To our knowledge, only @Liu2014 consider both pre-copulatory and post-copulatory inbreeding avoidance jointly, finding evidence of pre-copulatory, but not post-copulatory, inbreeding avoidance in cabbage beetles (*Colaphellus bowringi*). Taken together, all of these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature. However, there is as yet no theory that predicts what combinations should be favoured by selection when polyandry and pre-copulatory and post-copulatory inbreeding avoidance can all potentially evolve. Consequently, there is no theory that allows the diversity of existing empirical results to be rationalised or interpreted, and no clear hypotheses that could be tested with these studies through comparative analyses or that could be applied to future empirical studies of individual systems.

>>>>

Despite the paucity of theory and resulting predictions, numerous empirical studies on diverse species have tested for, and found evidence of, female inbreeding avoidance in systems where polyandry also occurs. However, relatively few studies have determined whether inbreeding avoidance is enacted through pre-copulatory or post-copulatory mechanisms. Pre-copulatory inbreeding avoidance has been reported in diverse species, spanning sweet potato weevils [*Cylas formicarius*, @Kuriwada2011], purple-crowned fairy-wrens [*Malurus coronatus*, @Kuriwada2011], and a tropical butterfly [*Bicyclus anynana*, @Fischer2015], while post-copulatory inbreeding avoidance has been reported in species including red junglefowl [*Gallus gallus*, @Pizzari2004] and crickets [*Teleogryllus oceanicus*, @Simmons2006; *Gryllus bimaculatus*, @Bretman2009]. Evidence for both pre-copulatory and post-copulatory inbreeding avoidance is available across different studies of Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015]. Meanwhile, @Liu2014 found evidence of pre-copulatory but not post-copulatory inbreeding avoidance within a single study of cabbage beetles (*Colaphellus bowringi*). However, @Ala-Honkola2011 and @Tan2012 found no evidence for pre-copulatory or post-copulatory inbreeding avoidance in fruit flies (*Drosophila melanogaster*), respectively, and Reid et al. [-@Reid2014; -@Reid2015] found no net inbreeding avoidance in song sparrows (*Melospiza melodia*) despite strong inbreeding depression. Taken together, these studies demonstrate that diverse combinations of pre-copulatory and post-copulatory inbreeding avoidance occur in nature alongside polyandry. However, there is as yet no theory that predicts what combinations of pre-copulatory and post-copulatory inbreeding avoidance and polyandry should be favoured by selection when all combinations of phenotypes can evolve. Consequently, there is no theory that allows the diversity of existing empirical results regarding pre-copulatory and post-copulatory inbreeding avoidance to be rationalised or interpreted, and no clear hypotheses that could be tested through future empirical studies of individual systems or subsequent comparative analyses.

<!--- I don't know of any review articles or meta-analyses that look at polyandry to avoid inbreeding. At least, none within the last 10 years. --->
<!--- I'm not sure I understand the point of ''tractable systems'' for post-copulatory inbreeding avoidance -- why not just 'species', as with pre-copulatory? --->
<!--- What is the difference between 'rationalised' and 'interpreted'? Do these refer to the same thing, and if so, can we get rid of 'rationalised'? --->
<!--- I still think that the end of this paragraph misses the point a bit with regard to how theory is supposed to function. --->

@@
